---
title: "Work Sheet 6"
author: "Wendy Nalaza"
date: "2022-11-25"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

***Use the dataset mpg***

```{r}
library(ggplot2)
data(mpg)
as.data.frame(data(mpg))
```

**data(mpg)**

```{r, data1}
data("mpg")
str("mpg")
library(dplyr)
glimpse(mpg)
```



***Example. graph using ggplot()***

**ggplot(mpg, aes(cty, hwy)) +
  geom_point()**

***1. How many columns are in mpg dataset? How about the number of rows? Show the codes and its result.***
*ANSWER: The total of columns are 11 columns and 234 rows*

```{r echo=TRUE}
ROW <- nrow(mpg)
COLUMN <-ncol(mpg)
ROW
COLUMN
```


***2. Which manufacturer has the most models in this data set? Which model has the most variations?***

```{r x2, echo=FALSE}
Manufacturer <- mpg %>% 
  group_by(manufacturer) %>% 
  tally(sort = TRUE)

Manufacturer
```
*ANSWER: Dodge and has 37 models*

**a. Group the manufacturers and find the unique models. Copy the codes and result.**

```{r echo=TRUE}
DATAmpg <- mpg
Manufacturer2 <- DATAmpg %>% group_by(manufacturer, model) %>%
  distinct() %>% count()
Manufacturer2

colnames(Manufacturer2) <- c("Manufacturer", "Model","Counts")
Manufacturer2
```

**b. Graph the result by using plot() and ggplot(). Write the codes and its result.**

+
**plot**
```{r echo=TRUE}
qplot(model, data = mpg,geom = "bar", fill=manufacturer)
```

+
**ggplot**
```{r echo=TRUE}
ggplot(mpg, aes(model, manufacturer)) + geom_point()
```

**3. Same dataset will be used. You are going to show the relationship of the model and the manufacturer.**

```{r echo=TRUE}
DATAmpg <- mpg
Manufacturer3 <- DATAmpg %>% group_by(manufacturer, model) %>%
  distinct() %>% count()

Manufacturer3

colnames(Manufacturer3) <- c("Manufacturer", "Model")
Manufacturer3
```

***a. What does ggplot(mpg, aes(model, manufacturer)) + geom_point() show?***

```{r echo=FALSE}
ggplot(mpg, aes(model, manufacturer)) + geom_point()
```

*ANSWER: Geometric point graph of mpg(model and manufacturer)*

***b. For you, is it useful? If not, how could you modify the data to make it more informative? ***
*ANSWER: Yes, it is helpful since you can track down and edit each model's data directly from the manufacturer.*
+
**to modify the data:**
```{r echo=TRUE}
ggplot(mpg, aes(model, manufacturer)) + 
  geom_point() +
  geom_jitter()
```
***4. Using the pipe (%>%), group the model and get the number of cars per model.Show codes and its result.***

```{r echo=TRUE}
DATAmpg4 <- Manufacturer2 %>% group_by(Model) %>% count()
DATAmpg4

colnames(DATAmpg4) <- c("Model","Counts")
```

**a. Plot using the geom_bar() + coord_flip() just like what is shown below. Show codes and its result**

```{r echo=TRUE}
qplot(model,
      data = mpg,main = "Number of Cars per Model", 
      xlab = "Model",
      ylab = "Number of Cars", 
      geom = "bar", fill = manufacturer
      + coord_flip())
```

**b. Use only the top 20 observations. Show code and results.**

```{r echo=TRUE}
Top_Data <- DATAmpg4[1:20,]%>%top_n(2)
Top_Data
ggplot(Top_Data,aes(x = Model,y =Counts)) + geom_bar(stat = "Identity") + coord_flip()
```

***5. Plot the relationship between cyl - number of cylinders and displ - engine displacement using geom_point with aesthetic colour = engine displacement.Title should be “Relationship  between No. of Cylinders and Engine Displacement”.***

**a. Show the codes and its result.**

```{r echo=TRUE}
ggplot(data = mpg , mapping = aes(x = displ, y = cyl, 
      main = "Relationship between No of Cylinders and Engine Displacement")) + 
  geom_point(mapping=aes(colour = "engine displacement")) + geom_jitter()
```

**b. How would you describe its relationship?**

*ANSWER: So according to the data, by making cyl into y, the graph is scattered, and the pink color indicates the engine displacement, as you can see from the dots in a straight horizontal position.*

***6.Get the total number of observations for drv - type of drive train (f = front-wheel drive,r = rear wheel drive, 4 = 4wd) and class - type of class (Example: suv, 2seater, etc.) Plot using the geom_tile() where the number of observations for class be used as a fill for aesthetics.***

**a. Show the codes and its result for the narrative in 6.**

```{r echo=TRUE}
ggplot(data = mpg, mapping = aes(x = drv, y = class)) + 
  geom_point(mapping=aes(color=class)) +
  geom_tile()
```

**b. Interpret the result: **

*ANSWER : Areas covered with black are "mapped" using the mapping geometric point graph, with y as class and x as drv.*

***7. Discuss the difference between these codes. Its outputs for each are shown below.***

+
**Code 1**

```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy, colour = "blue"))
```

+
**+ Code 2**

```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy), colour = "blue")
```

***8. Try to run the command ?mpg. What is the result of this command?***

```{r}
?mpg
```
*The result of the command are the server website and the data of mpg.*

**a. Which variables from mpg dataset are categorical? **

*ANSWER: Categorical variables in mpg which include: the manufacturer, model, trans (type of transmission), drv (front-wheel drive, rear-wheel, 4wd), fl (fuel type), and class (type of car).*

**b. Which are continuous variables?**
*ANSWERS: Continuous varibles in R were also known as doubles or integers. *

**c. Plot the relationship between displ (engine displacement) and hwy(highway miles per gallon). Mapped it with a continuous variable you have identified in 5-b.**

```{r echo=TRUE}
ggplot(mpg, aes(x = cty, y = hwy, colour = displ)) + geom_point()
```

**What is its result? Why it produced such output? **
*ANSWER: Data tracks the cty by showing (city miles per gallon) in a color with a blue hue or variation of blue.*

***9.Plot the relationship between displ (engine displacement) and hwy(highway miles per gallon) using geom_point(). Add a trend line over the existing plot using geom_smooth() with se = FALSE. Default method is “loess”.***

```{r echo=TRUE}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) +
  geom_point(mapping=aes(color=class)) +
  geom_smooth(se = FALSE)
```

***10.Using the relationship of displ and hwy, add a trend line over existing plot. Set the se = FALSE to remove the confidence interval and method = lm to check for linear modeling***

```{r echo=TRUE, message=FALSE, warning=FALSE}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy, color = class)) +
  geom_point() +
  geom_smooth(se = FALSE)
```