---
title: "Work Sheet 3b"
author: "Wendy Nalaza"
date: "2022-11-22"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

***Worksheet-3b in R***

*Instructions:*

**Use RStudio or the RStudio Cloud accomplish this worksheet.**

*Save the R script as RWorksheet_lastname 3b.R.*

*On your own GitHub repository, push the R script, the Rmd file, as well as this*
*pdf worksheet to the repo you have created before.*

*Do not forget to comment your Git repo on our VLE*

*Accomplish this worksheet by answering the questions being asked and writing*
*the code manually.*

install.packages("dplyr")
library(dplyr)
library(tidyverse)

***1. Create a data frame using the table below.***
 
**a.Write the codes.**
 
```{r x1}
Residents <- data.frame(
  Respondents = c(1:20),
  sex = c(2, 2, 1, 2, 2, 2, 2, 2, 2, 2, 1, 2, 2, 2, 2, 2, 2, 2, 1, 2),
  Fathers_Occupation = c(1, 3, 3, 3, 1, 2, 3, 1, 1, 1, 3, 2, 1, 3, 3, 1, 3, 1, 2, 1),
  Persons_at_Home = c(5, 7, 3, 8, 5, 9, 6, 7, 8, 4, 7, 5, 4, 7, 8, 8, 3, 11, 7, 6),
  Siblings_at_school = c(6, 4, 4, 1, 2, 1, 5, 3, 1, 2, 3, 2, 5, 5, 2, 1, 2, 5, 3, 2),
  Types_of_Houses = c(1, 2, 3, 1, 1, 3, 3, 1, 2, 3, 2, 3, 2, 2, 3, 3, 3, 3, 3, 2))
```

**b.Describe the data. Get the structure or the summary of the data**

>
Answer: Declaring the object as a "resident" and using the function data frames to collect the variables of respondents and make matrices and lists

```{r x1, B}
summary(Residents)
```

**c. Is the mean number of siblings attending is 5?**

"Answer: No"

**d. Extract the 1st two rows and then all the columns using the subsetting functions.**
**Write the codes and its output.**

```{r echo=TRUE}
Subset <- subset(Residents[1:2, 1:6, drop = FALSE])
Subset
```

**e. Extract 3rd and 5th row with 2nd and 4th column. Write the codes and its result.**
 
```{r echo=TRUE}
Subset1 <- subset(Residents[c(3,5),c(2,4)])
Subset1
```

**f. Select the variable types of houses then store the vector that results as types_houses.**
**Write the codes.**
 
```{r, 1F}
Store <- Residents[c(6)]
type_of_houses <- Store

```

**g. Select only all Males respondent that their father occupation was farmer. Write**
**the codes and its output.**
 
```{r echo=TRUE}
subset(Residents, sex == 1, select = Fathers_Occupation == 1)

```




**h. Select only all females respondent that have greater than or equal to 5 number**
**of siblings attending school. Write the codes and its outputs**

```{r x1, H}
females <- subset(Residents[c(1:20), c(2,5)])
```
```{r echo=TRUE}
girls <- females[Residents$Siblings_at_school >= 5,]
girls
```

 ***2. Write a R program to create an empty data frame. Using the following codes:***
 
```{r echo=TRUE}
  dtframe = data.frame(Ints=integer(),
                  Doubles=double(), Characters=character(),
                  Logicals=logical(),
                  Factors=factor(),
                  stringsAsFactors=FALSE)
print("Structure of the empty dataframe:")
print(str(dtframe))
```