---
title: "Individual Project 2"
author: "Wendy Nalaza"
date: "2022-12-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#Packages applied
```{r echo=TRUE}
library("twitteR")
library(tm)
library(dplyr)
library("plotly")
library(ggplot2)
library(RColorBrewer)
library(tidytext)
library(stringr)
library(tidyr)
library(rtweet)
library(corpus)
library(magrittr)
library(wordcloud)
library(wordcloud2)
library(syuzhet)
```

#set the directory to save data
```{r echo=TRUE}
setwd("C:/CS101_DATA_SCIENCE/Nalaza_Repo/Individual Project/Individual Project 2")
```
#Extract from twitter using your developer's credentials.
```{r echo=TRUE}
CONSUMER_SECRET <- "gbuzairwHJDlzG6zmK3fFxqcEo2GIHbRy89NISU80IaqvVhjIx"
CONSUMER_KEY <- "s2yMTMlykz9iJ2I86kHzWsqtF"
ACCESS_SECRET <- "znEI53FQ3P1xhF3BAfvwiptXKtTMSAmD9BTzozQD8ax98"
ACCESS_TOKEN <- "1598161218618867713-qojQanThDqRQOlGJ4YcCXhFkYDx1gr"
```

```{r echo=TRUE}
setup_twitter_oauth(consumer_key = CONSUMER_KEY,
                    consumer_secret = CONSUMER_SECRET,
                    access_token = ACCESS_TOKEN,
                    access_secret = ACCESS_SECRET)
```
#Get 10000 observations including retweets


trendTweets <- searchTwitter("#TheGameAwards",
                             n = 10000,
                             lang = "en",
                             since = "2022-12-01",
                             until = "2022-12-08",
                             retryOnRateLimit=120)
                             
#Converting data into dataframe

TrendTweetsDF <- twListToDF(trendTweets)

#Saving File

save(TrendTweetsDF,file = "TrendTweetsDF.Rdata")

#using the existed data
```{r echo=TRUE}
load(file = "TrendTweetsDF.Rdata")
```

#Subset the retweets and the original tweets into a separate file
#Plot the retweets and the original tweets using bar graph in vertical manner and include legends

#Original Tweets
```{r echo=TRUE}
Original <- subset(TrendTweetsDF, isRetweet=="FALSE",
                         select= c(text,screenName,created, isRetweet))

Original %>%
  group_by(1) %>%
  summarise(max = max(created), min= min(created))


Tweets <- Original %>%  mutate(Created_At_Round = 

             created %>% round(units = 'hours') %>% as.POSIXct())
```
```{r echo=TRUE}
Minimum <- Tweets %>% pull(created) %>% min()
Minimum

Maximum <- Tweets %>% pull(created) %>% max()
Maximum

```
#Plot of the original tweets

```{r echo=TRUE}
Original_tweets <- ggplot(Tweets, aes(x = created)) +
  geom_histogram(aes(fill = ..count..)) +
  theme(legend.position = "right") +
  xlab("Time") + ylab("Number of tweets") + 
  scale_fill_gradient(low = "midnightblue", high = "purple") + 
  labs(title = "The Original Tweets", subtitle = "December 7,2022")

Original_tweets %>% ggplotly()
```
#The Retweets
```{r echo=TRUE}
Retweets <- subset(TrendTweetsDF, isRetweet=="TRUE",
                   select= c(text,screenName,created, isRetweet))

Retweets %>%  
  group_by(1) %>%  
  summarise(max = max(created), min = min(created))

Retweets_1 <- Retweets %>% mutate(Created_At_Round = created%>% 
                            round(units = 'hours') %>%
                            as.POSIXct())
```

```{r echo=TRUE}
mini <- Retweets_1 %>% pull(created) %>% min()
mini
maxi <- Retweets_1 %>% pull(created) %>% max()
maxi
```
#Plot of the retweets
```{r echo=TRUE}
Retweets_2<- ggplot(Retweets_1, aes(x = created)) +
  geom_histogram(aes(fill = ..count..)) +
  theme(legend.position = "right") +
  xlab("Time") + ylab("Number of Retweets") + 
  scale_fill_gradient(low = "midnightblue", high = "skyblue") +
  labs(title = "The Retweets", subtitle = "December 7,2022")

Retweets_2 %>% ggplotly()
```